Supplementary Material for Asymmetry paper

### 2020-06-09 Supplementary/Sup_mat.Rmd

gridExtra::grid.arrange(plt_hist, plt_dists, ncol = 2)

@@

# make plot 
plt_dists_wP <- df_part2 %>%
  ggplot(aes(beta_pos)) + 
  geom_histogram(aes(y = ..density..),
                 # binwidth = .1
                 ) + 
  geom_line(data = df_dists,
            aes(x_vals, y,
                colour = increase)) + 
  see::scale_color_flat() + 
  scale_x_continuous(expression(paste("Normalised ", Delta, sep = " "))) +
  theme_bw() + 
  theme(strip.text.x = element_blank()) + 
  facet_wrap(~Participant, scales = "free")

>>>>

# gridExtra::grid.arrange(plt_hist, plt_dists, ncol = 2)

@@

# make plot 
plt_dists_wP <- df_part2 %>%
  ggplot(aes(beta_pos)) + 
  geom_histogram(aes(y = ..density..),
                 # binwidth = .1
                 ) + 
  geom_line(data = df_dists,
            aes(x_vals, y,
                colour = increase)) + 
  see::scale_color_flat() + 
  scale_x_continuous(expression(paste("Normalised ", Delta, sep = " "))) +
  theme_bw() + 
  theme(strip.text.x = element_blank()) + 
  facet_wrap(~Participant, scales = "free")
plt_dists_wP
```
